---
output:
  github_document: default
  html_document: default
---
--
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# phylogenies

<!-- badges: start -->
<!-- badges: end -->

The goal of phylogenies is to visualize cancer phylogenies, also introduce using new point shape (upside down half-triangle) for visualization. 

## Installation

You can install the development version of phylogenies from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Leslie2101/phylogenies")
```

## Example

This is a basic example which shows you how to solve a common problem:


### 1. Visualizing driver-annotated PyClone 
```{r example}
library(phylogenies)
data <- sample_pyclone_data
print(head(data, 3))
make_pyclone_donut_plot(data)

```

### 2. Make half-triangle plot
```{r half}
df <- data.frame(x = 1:5,
                 y1 = 1:5,
                 y2 = 1:5,
                 z1 = seq(10, 50, length.out=5),
                z2 = seq(50, 10, length.out=5))
make_half_triangle_plot(df, x = as.factor(x),
                         y_1= y1, y_2= y2,
                         z_1 = z1, z_2 = z2)

```

### 3. Make full-triangle plot
```{r full}
set.seed(123) # For reproducibility
df <- data.frame(
  x = 1:10,
  y1 = sample(1:10, 10, replace = TRUE),
  y2 = sample(1:10, 10, replace = TRUE),
  z1 = sample(1:10, 10, replace = TRUE),
  z2 = sample(1:10, 10, replace = TRUE)
)

make_full_triangle_plot(df, x = as.factor(x), y_1= y1, y_2=y2, z_1 = z1, z_2 = z2)

```

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. -->

<!-- In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN. -->
